Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-07-20 drafts/outline.tex
minor edits throughout

We used wooden dowels as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel. The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-section. Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.

>>>>

We used 1/8" wooden dowels ($d_c = \SI{.3175}{\centi\metre}$) as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel. The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-section.

Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps. %TODO sed trap paragraph
